---
title: "Comparisons across NEUS Rpath models"
author: "Sarah J. Weisberg"
date: "2024-03-18"
output: html_document
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#0 Prep
    Load packages and models for analysis
```{r}
#data organizing and wrangling
library(here)
library(dplyr)
library(tidyr)
library(forcats)
library(data.table)

#plotting
library(RColorBrewer)
library(ggspatial)
library(gridExtra)
library(ggplot2)
library(ggbeeswarm)
library(showtext)
library(igraph)
library(ggnetwork)
library(viridis)

#spatial tools
remotes::install_github('NEFSC/NEFSC-Spatial')
library(NEFSCspatial)
library(sf)
library(rnaturalearth)
library(rmapshaper)
library(marmap)

#Rpath, enaR
library(devtools)
install.packages("gdata", repos = "https://packagemanager.posit.co/cran/2023-05-06") #need to install an older version of gdata for enaR to install properly
install_github('SEELab/enaR', force = T)
library(gdata)
library(enaR)
library(sna)
remotes::install_github('NOAA-EDAB/Rpath')
library(Rpath)

#stats tools
library(stats)

```
Load in the balanced models from Github
```{r}
#GB
load(url("https://github.com/NOAA-EDAB/GBRpath/blob/master/data/GB_balanced_params.RData?raw=true"))

#GOM
load(url("https://github.com/SarahJWeisberg/GOM-Rpath/blob/main/outputs/GOM_Rpath.RData?raw=true"))
load(url("https://github.com/SarahJWeisberg/GOM-Rpath/blob/main/outputs/GOM_params_Rpath.RData?raw=true"))

#MAB
load(url("https://github.com/Nyelab/MAB-Rpath/blob/balance_prep/outputs/MAB_params_Rpath_no_disc.RData?raw=true"))
load(url("https://github.com/Nyelab/MAB-Rpath/blob/balance_prep/outputs/MAB_Rpath_no_disc.RData?raw=true"))
```

#1 Ecological Network Analysis (ENA)

##1.1 Convert starting models to networks
```{r}
#MAB
#Set up model with group names and types
groups<-as.vector(MAB.rpath$Group)

#Count number of each group type
nliving <- nrow(MAB.rpath.params$model[Type <  2, ])
ndead   <- nrow(MAB.rpath.params$model[Type == 2, ])

#find index of pp
pp <- which(groups == "Phytoplankton")

#pull diet
diet<-MAB.rpath$DC
#Get consumption values by DC*QB*Biomass
QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
for (j in 1:nliving){
  QQ[,j]<-diet[,j]*MAB.rpath$QB[j]*MAB.rpath$Biomass[j]
}
#Ignore Imports
QQ<-QQ[1:(nliving+ndead),]
colnames(QQ)<-groups[1:nliving]
rownames(QQ)<-groups[1:(nliving+ndead)]
#Calculate flow to detritus
M0<-MAB.rpath$PB*(1-MAB.rpath$EE)
Detritus<-(M0*MAB.rpath$Biomass+MAB.rpath$QB*MAB.rpath$Biomass*MAB.rpath$Unassim)*MAB.rpath$DetFate[,1]
Detritus<-Detritus[1:(nliving+ndead)]
#Flow to detritus from detritus = 0
Detritus[(nliving+1)]<-0
#Bind diet matrix (QQ) with flow to detritus, discards
QQ<-cbind(QQ,Detritus)
#Calculate exports
#First sum catch
Catch<-rowSums(MAB.rpath$Landings)
#Add positive biomass accumulation terms
Export<-Catch+(ifelse(MAB.rpath$BA>0,MAB.rpath$BA*MAB.rpath$Biomass,0))
Export<-Export[1:(nliving+ndead)]
for (i in 1:ndead){
  Export[nliving+i]<-M0[nliving+i]*MAB.rpath$Biomass[nliving+i]
}
#Calculate respiration
#Assume detritus, discards have 0 respiration
Resp<-((1-MAB.rpath$Unassim)*MAB.rpath$QB-MAB.rpath$PB)*MAB.rpath$Biomass
Resp<-ifelse(Resp>0,Resp,0)
Resp<-Resp[1:(nliving+ndead)]
Resp[(nliving+1):(nliving+ndead)]<-0
#Deal with Primary Production
#First, estimate GROSS production = Imports
#P/B in Ecopath model gives NET production
#Ratio of gross:net is going to be fixed based on EMAX
gross_net<-(4251.874+1062.968)/4251.874
gross<-gross_net*MAB.rpath$PB[pp]*MAB.rpath$Biomass[pp]
Resp[pp]<-gross-(MAB.rpath$PB[pp]*MAB.rpath$Biomass[pp])
#Calculate imports
#Negative biomass accumulation terms
#Gross primary production
Import<-abs(ifelse(MAB.rpath$BA<0,MAB.rpath$BA*MAB.rpath$Biomass,0))
Import[pp]<-gross
Import<-Import[1:(nliving+ndead)]
#Trim biomass
Biomass<-MAB.rpath$Biomass[1:(nliving+ndead)]
#Pack the model directly and store
orig.network_MAB<-enaR::pack(flow = QQ,
                         input = Import,
                         export = Export,
                         living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                         respiration = Resp,
                         storage = Biomass)

#GOM
#Set up model with group names and types
groups<-as.vector(GOM$Group)

#Count number of each group type
nliving <- nrow(GOM.params$model[Type <  2, ])
ndead   <- nrow(GOM.params$model[Type == 2, ])

#Find index of pp groups
pp<- which(groups == "Phytoplankton")

#Pull diet matrix
diet<-GOM$DC
#Get consumption values by DC*QB*Biomass
QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
for (j in 1:nliving){
  QQ[,j]<-diet[,j]*GOM$QB[j]*GOM$Biomass[j]
}
#Ignore Imports
QQ<-QQ[1:(nliving+ndead),]
colnames(QQ)<-groups[1:nliving]
rownames(QQ)<-groups[1:(nliving+ndead)]
#Calculate flow to detritus
M0<-GOM$PB*(1-GOM$EE)
Detritus<-(M0*GOM$Biomass+GOM$QB*GOM$Biomass*GOM$Unassim)*GOM$DetFate[,1]
#Detritus<-GOM$QB*GOM$Biomass*GOM$Unassim
Detritus<-Detritus[1:(nliving+ndead)]
#Note that I am ignoring discards here
#Flow to detritus from detritus = 0
Detritus[(nliving+1)]<-0
#Bind diet matrix (QQ) with flow to detritus, discards
QQ<-cbind(QQ,Detritus)
#Calculate exports
#First sum catch
Catch<-rowSums(GOM$Landings)
#Add positive biomass accumulation terms
Export<-Catch+(ifelse(GOM$BA>0,GOM$BA,0))
Export<-Export[1:(nliving+ndead)]
for (i in 1:ndead){
  Export[nliving+i]<-GOM$PB[(nliving+i)]*GOM$Biomass[(nliving+i)]
}
#Calculate respiration
#Assume detritus, discards have 0 respiration
Resp<-((1-GOM$Unassim)*GOM$QB-GOM$PB)*GOM$Biomass
Resp<-ifelse(Resp>0,Resp,0)
Resp<-Resp[1:(nliving+ndead)]
Resp[(nliving+1):(nliving+ndead)]<-0
#Deal with Primary Production
#First, estimate GROSS production = Imports
#P/B in Ecopath model gives NET production
#Ratio of gross:net is going to be fixed based on EMAX
gross_net<-4101.9/3281.5
gross<-gross_net*GOM$PB[1]*GOM$Biomass[1]
Resp[1]<-gross-(GOM$PB[1]*GOM$Biomass[1])
#Calculate imports
#Negative biomass accumulation terms
#Gross primary production
Import<-abs(ifelse(GOM$BA<0,GOM$BA,0))
Import[1]<-gross
Import<-Import[1:(nliving+ndead)]
#Trim biomass
Biomass<-GOM$Biomass[1:(nliving+ndead)]
#Pack the model directly and store
orig.network_GOM<-enaR::pack(flow = QQ,
                         input = Import,
                         export = Export,
                         living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                         respiration = Resp,
                         storage = Biomass)
```
##1.2 ENA on starting models
```{r}
orig.networks$GOM<-orig.network_GOM
info.orig_GOM<-enaAscendency(orig.network_GOM)
info.orig_GOM <- as.data.frame(info.orig_GOM)
orig.networks$MAB<-orig.network_MAB
orig.info<-lapply(orig.networks, enaAscendency)
```

#2 Analyze and compare ecosense outputs
  Load ecosense outputs - bounded and unbounded
```{r}
#load ecosense outputs
#need to adjust these file names to be more concise
#MAB
load(url("https://github.com/Nyelab/MAB-Rpath/blob/balance_prep/outputs/MAB_sense_50k_2024_no_disc.RData?raw=true"))

#GOM
#with thermodynamic bounding
load(url("https://github.com/SarahJWeisberg/GOM-Rpath/blob/main/outputs/GOM_sense_50k_resp_constrain.RData?raw=true"))
#without thermodynamic bounding
load(url("https://github.com/SarahJWeisberg/GOM-Rpath/blob/main/outputs/GOM_sense_unbound.RData?raw=true"))
```

#3 ENA on Ecosense outputs
##3.1 Network conversion of MAB ecosense outputs
```{r}
#Copy initial Rpath parameters
#Alternative scenarios will be the same except for Biomass, PB, QB, Diet, M0
alt<-copy(MAB.rpath.params)
alt.diet<-copy(MAB.rpath.params$diet)

#Set up model with group names and types
groups<-as.vector(MAB.rpath$Group)
#Count number of each group type
ngroups <- nrow(alt$model)
nliving <- nrow(alt$model[Type <  2, ])
ndead   <- nrow(alt$model[Type == 2, ])
ngear   <- nrow(alt$model[Type == 3, ])
#find index of pp
pp <- which(groups == "Phytoplankton")

#calculate ena metrics for all ecosense outputs
alt.networks<-as.list(rep(NA,length(MAB_sense)))

for (i in 1:length(alt.networks)) {
  #Copy initial Rpath parameters
  Rpath.alt<-copy(MAB.rpath.params)
  #Copy scenario
  MAB.alt<-MAB_sense[[i]]
  #Assign biomass
  #Ignore Outside
  Biomass<-MAB.alt$B_BaseRef[2:(nliving+ndead+1)]
  #Assign PB
  PB<-MAB.alt$PBopt[2:(nliving+ndead+1)]
  #Assign QB
  QB<-MAB.alt$FtimeQBOpt[2:(nliving+ndead+1)]
  QB[pp]<-0
  #Assign M0
  M0<-MAB.alt$MzeroMort[2:(nliving+ndead+1)]
  #Assign diet
  #Remove first two entries which represent 'outside' flow to 'outside' and 'PP'
  PreyFrom<-MAB.alt$PreyFrom[-c(1,2)]
  PreyTo<-MAB.alt$PreyTo[-c(1,2)]
  predpreyQ<-MAB.alt$QQ[-c(1,2)]
  #Fill consumption matrix
  QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
  for (j in 1:length(PreyFrom)){
    prey<-PreyFrom[j]
    pred<-PreyTo[j]
    QQ[prey,pred]<-predpreyQ[j]
  }
  #convert NAs to 0s
  QQ[which(is.na(QQ)==T)]<-0
  #Ignore Imports
  QQ<-QQ[1:(nliving+ndead),]
  colnames(QQ)<-groups[1:nliving]
  rownames(QQ)<-groups[1:(nliving+ndead)]
  #Calculate flows to detritus
  Unassim<-MAB.alt$UnassimRespFrac[2:(nliving+ndead+1)]
  DetFate<-MAB.alt$DetFrac[2:(nliving+ndead+1)]
  Detritus<-(M0*Biomass+QB*Biomass*Unassim)*DetFate
  #Detritus<-(model$QB*model$Biomass*model$Unassim)*model$DetFate[,1]
  #Detritus<-Detritus[1:(nliving+ndead)]
  #Deal with flow to detritus from discards
  #Should be equal to all flow to discards minus consumption by SeaBirds(45)
  #DetInDisc<-sum(Discards)
  #Detritus[58]<-DetInDisc-QQ[58,45]
  #Flow to detritus from detritus = 0
  Detritus[(nliving+ndead)]<-0
  #Bind diet matrix (QQ) with flow to detritus, discards
  QQ<-cbind(QQ,Detritus)
  #Calculate exports
  #First sum catch
  Catch<-rowSums(MAB.rpath$Landings)[1:(nliving+ndead)]
  #Add positive biomass accumulation terms
  BA<-MAB.rpath$BA[1:(nliving+ndead)]
  Export<-Catch+(ifelse(BA>0,BA*Biomass,0))
  for (k in 1:ndead){
    Export[nliving+k]<-M0[nliving+k]*Biomass[nliving+k]
  }
  Export<-Export[1:(nliving+ndead)]
  #Calculate respiration
  #Assume detritus, discards have 0 respiration
  Resp<-((1-Unassim)*QB-PB)*Biomass
  Resp<-ifelse(Resp>0,Resp,0)
  Resp<-Resp[1:(nliving+ndead)]
  Resp[(nliving+1):(nliving+ndead)]<-0
  #Deal with Primary Production
  #First, estimate GROSS production = Imports
  #P/B in Ecopath model gives NET production
  #Ratio of gross:net is going to be fixed based on EMAX
  gross_net<-(4251.874+1062.968)/4251.874
  gross<-gross_net*PB[pp]*Biomass[pp]
  Resp[pp]<-gross-(PB[pp]*Biomass[pp])
  #Calculate imports
  #Negative biomass accumulation terms
  #Gross primary production
  Import<-abs(ifelse(BA<0,BA*Biomass,0))
  #EE_Biomass<-ifelse(model$EE>1,(model$EE-1)*model$Biomass,0)
  #Import<-BA_Biomass+EE_Biomass
  Import[pp]<-gross
  Import<-Import[1:(nliving+ndead)]
  #Pack the model directly and store
  alt.networks[[i]]<-enaR::pack(flow = QQ,
                                input = Import,
                                export = Export,
                                living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                                respiration = Resp,
                                storage = Biomass)
}

MAB_info<-lapply(alt.networks, enaAscendency)
rm(alt.networks)
```
##3.3 Network conversion of GOM ecosense outputs
```{r}
#Copy initial Rpath parameters
#Alternative scenarios will be the same except for Biomass, PB, QB, Diet, M0
alt<-copy(GOM.params)
alt.diet<-copy(GOM.params$diet)
#Set up model with group names and types
groups<-as.vector(GOM$Group)
#Count number of each group type
ngroups <- nrow(alt$model)
nliving <- nrow(alt$model[Type <  2, ])
ndead   <- nrow(alt$model[Type == 2, ])
ngear   <- nrow(alt$model[Type == 3, ])
#find index of pp
pp <- which(groups == "Phytoplankton")

#bind bounded and unbounded outputs
senses<-c(GOM_sense,GOM_sense_unbound)
#generate network models
alt.networks<-as.list(rep(NA,length(senses)))

#start with thermodynamically bound outputs
for (i in 1:length(senses)) {
  model<-senses[[i]]
  #Assign biomass, ignore Outside
  Biomass<-model$B_BaseRef[2:(nliving+ndead+1)]
  #Assign PB
  PB<-model$PBopt[2:(nliving+ndead+1)]
  #Assign QB
  QB<-model$FtimeQBOpt[2:(nliving+ndead+1)]
  QB[pp]<-0
  #Assign M0
  M0<-model$MzeroMort[2:(nliving+ndead+1)]
  #Assign diet
  #Remove first two entries which represent 'outside' flow to 'outside' and 'PP'
  PreyFrom<-model$PreyFrom[-c(1,2)]
  PreyTo<-model$PreyTo[-c(1,2)]
  predpreyQ<-model$QQ[-c(1,2)]
  #Fill consumption matrix
  QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
  for (j in 1:length(PreyFrom)){
    prey<-PreyFrom[j]
    pred<-PreyTo[j]
    QQ[prey,pred]<-predpreyQ[j]
  }
  #convert NAs to 0s
  QQ[which(is.na(QQ)==T)]<-0
  #Ignore Imports
  QQ<-QQ[1:(nliving+ndead),]
  colnames(QQ)<-groups[1:nliving]
  rownames(QQ)<-groups[1:(nliving+ndead)]
  #Calculate flows to detritus
  Unassim<-model$UnassimRespFrac[2:(nliving+ndead+1)]
  DetFate<-model$DetFrac[2:(nliving+ndead+1)]
  Detritus<-(M0*Biomass+QB*Biomass*Unassim)*DetFate
  #Flow to detritus from detritus = 0
  Detritus[(nliving+ndead)]<-0
  #Bind diet matrix (QQ) with flow to detritus, discards
  QQ<-cbind(QQ,Detritus)
  #Calculate exports
  #First sum catch
  #Catch doesn't change in Ecosense so am pulling from original model
  Catch<-rowSums(GOM$Landings)[1:(nliving+ndead)]
  #Add positive biomass accumulation terms
  BA<-GOM$BA[1:(nliving+ndead)]
  Export<-Catch+(ifelse(BA>0,BA*Biomass,0))
  for (k in 1:ndead){
    Export[nliving+k]<-M0[(nliving+k)]*Biomass[(nliving+k)]
  }
  Export<-Export[1:(nliving+ndead)]
  #Calculate respiration
  #Assume detritus, discards have 0 respiration
  Resp<-((1-Unassim)*QB-PB)*Biomass
  Resp<-ifelse(Resp>0,Resp,0)
  Resp<-Resp[1:(nliving+ndead)]
  Resp[(nliving+1):(nliving+ndead)]<-0
  #Deal with Primary Production
  #First, estimate GROSS production = Imports
  #P/B in Ecopath model gives NET production
  #Ratio of gross:net is going to be fixed based on EMAX
  gross_net<-4101.9/3281.5
  gross<-gross_net*PB[pp]*Biomass[pp]
  Resp[pp]<-gross-(PB[pp]*Biomass[pp])
  Import<-abs(ifelse(BA<0,BA*Biomass,0)) 
  Import[pp]<-gross
  Import<-Import[1:(nliving+ndead)]
  alt.networks[[i]]<-enaR::pack(flow = QQ,
                                input = Import,
                                export = Export,
                                living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                                respiration = Resp,
                                storage = Biomass)
}
```
##3.3 Comparing bounded/unbounded
```{r}
#pull nodal flows out of each alternate model
flow<-c()
for (i in 1:length(alt.networks)){
  alt.flow<-enaFlow(alt.networks[[i]],balance.override=T)
  flow_group<-cbind(groups[1:57],alt.flow$T)
  flow<-rbind(flow,flow_group)
}

#run ascendancy analysis on each alternate model
GOM_info<-lapply(alt.networks, enaAscendency)

rm(alt.networks)

#turn flows into dataframe
flow <- as.data.frame(flow)
rownames(flow)<-c()
colnames(flow)<-c("group","flow")
flow <- flow %>% mutate(flow=as.numeric(flow)) %>% 
  mutate(condition = c(rep("bounded",length(GOM_sense)*(nliving+ndead)),rep("unbounded",length(GOM_sense_unbound)*(nliving+ndead))))
#which flow distributions are not the same?
#test with Kolmogorov–Smirnov test
ks_flow<-c()
for(i in 1:(nliving+ndead)){
  bound<-flow %>% filter(group == groups[i],condition == "bounded")
  unbound<-flow %>% filter(group == groups[i], condition == "unbounded")
  test<-ks.test(bound$flow,unbound$flow)
  ks_flow<-rbind(ks_flow,c(groups[i],test$p.value))
}
ks_flow<-as.data.frame(ks_flow)
colnames(ks_flow)<-c("Group","p")
ks_flow$p<-as.numeric(ks_flow$p)

#how does A/C compare?
#Pick out relative ascendancy metric
ASC.CAP<-c()
for (i in 1:length(GOM_info)){
  ASC.CAP[i]<-GOM_info[[i]][[7]]
}
ASC.CAP<-as.data.frame(cbind(ASC.CAP,c(rep("bounded",length(GOM_sense)),rep("unbounded",length(GOM_sense_unbound)))))
ASC.CAP<- ASC.CAP %>% mutate(ASC.CAP = as.numeric(ASC.CAP)) %>% rename(condition = V2)

```


#4 Figures
## 4.1 Figure 1: Map
```{r}
bts<-NEFSCspatial::BTS_Strata

MAB_strata <- c(1010:1080, 1100:1120, 1600:1750, 3010:3450, 3470, 3500, 3510)
GB_strata  <- c(1090, 1130:1210, 1230, 1250, 3460, 3480, 3490, 3520:3550)
GOM_strata <- c(1220, 1240, 1260:1290, 1360:1400, 3560:3830)

bts_area<- bts %>% 
  mutate(EPU = ifelse(STRATA %in% MAB_strata,"MAB",ifelse(STRATA %in% GB_strata,"GB",ifelse(STRATA %in% GOM_strata,"GOM","other"))))

theme_set(theme_bw())

#load in countries for plotting 
world <- ne_countries(scale = "medium", returnclass = "sf")

#generate region outline polygons
Region <- bts_area %>% filter(!EPU == "other") %>%
  st_make_valid() %>% st_buffer(0) %>% group_by(EPU) %>% summarize()
Region <- ms_filter_islands(Region, min_area=10000000000) #get rid of that weird one in the gulf of maine 

# call in bathymetric data
# convert  bathymetric contours into dataframe
bathy <- getNOAA.bathy(-80, -64.5, 34, 46, resolution=1); bathydf <- as.xyz(bathy) 
#ignore positive depth (land)
bathy_sea <- bathydf; bathy_sea$V3[bathy_sea$V3 > 1] <- 0
#ignore depths greater than 500m
bathy_shelf<-bathy_sea %>% filter(V3 > -500) 

#make table of summary stats for each model
GOM_summary<-cbind(nrow(GOM.params$model[Type <  2, ]),nrow(GOM.params$model[Type == 3, ]))
GB_summary<-cbind(nrow(GB.params$model[Type <  2, ]),nrow(GB.params$model[Type == 3, ]))
MAB_summary<-cbind(nrow(MAB.rpath.params$model[Type <  2, ]),nrow(MAB.rpath.params$model[Type == 3, ]))
summary_stats<-data.frame(rbind(GOM_summary,GB_summary,MAB_summary))
rownames(summary_stats)<-c("GOM","GB","MAB")
colnames(summary_stats)<-c("Living Groups","Fleets")
tt<-ttheme_default(core=list(bg_params = list(fill=c("#377EB8","#FF7F00","#E41A1C"),alpha=0.7)))

#plot  
NEUS <- ggplot() +
  geom_sf(data = world)+
  geom_raster(data = bathy_shelf, aes(x = V1, y = V2, fill = V3)) +
  scale_fill_gradient(low="#586575", high="#daedf7",
                      breaks = c(-400,-250,-100),labels=c(400,250,100))+
  geom_sf(data = Region, fill = NA, linewidth = .5, aes(color=EPU))+
  scale_color_manual(values = c("#FF7F00","#377EB8","#E41A1C"))+
  geom_sf(data = world)+
  coord_sf(xlim =c(-78, -65.5), ylim = c(35, 45)) + #zoomed to Hatteras and N
  labs(x = NULL, y = NULL,fill= "Depth (m)") +
  guides(color="none",fill=guide_colorbar(reverse = T))+
  annotate("text",x=-72.5,y=38.5,label="MAB",size=4)+
  annotate("text", x = -71.5, y = 43, label = "GOM", size = 4)+
  annotate("text", x = -66, y = 41, label = "GB", size = 4)+
  annotation_custom(tableGrob(summary_stats,theme = tt),xmin=-69, xmax=-65.5, ymin=36.25, ymax=38)+
  ggspatial::annotation_scale(location = "br",bar_cols = c("grey60", "white")) +
  theme(plot.margin = margin(0, 0, 0, 0, "cm"),
        panel.grid.major = element_blank(),
        #panel.border = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(0.85,0.1),
        legend.title = element_text(face="italic"),
        legend.direction = "horizontal")

NEUS
```

##4.2 Figure 2: Network diagrams
```{r}
#start with MAB
#pull network structure
A<-enaStructure(orig.network_MAB)$A
g<-igraph::graph_from_adjacency_matrix(A)

groups_MAB<-MAB.rpath$Group
#Count number of each group type
nliving <- nrow(MAB.rpath.params$model[Type <  2, ])
ndead   <- nrow(MAB.rpath.params$model[Type == 2, ])

#get x and y coordinates
#derived from the plotfw function (https://rfrelat.github.io/BalticFoodWeb.html)
nylevel<-7 #determines number of levels along y-axis
n <- vcount(g) #number of vertices
tl<-MAB.rpath$TL[1:(nliving+ndead)] #pull trophic level calculations from rpath
bks <- c(0.9, seq(1.9, max(tl), length.out = nylevel))
ynod <- cut(tl, breaks = bks, include.lowest = TRUE, 
            labels = 1:(length(bks)-1)) #assign group to a y-level
maxx <- max(table(ynod)) #looks for max # of groups at any y-level
xnod <- rep(0,n)
for (i in 1:nylevel){
  l <- sum(ynod==i)
  
  ltr <- (l/maxx)**(1/2)*maxx
  if (l>1) {
    xnod[ynod==i] <- seq(-ltr,ltr,length.out = l)
  } else {
    xnod[ynod==i] <- 0
  }
}

coo <- cbind(xnod,tl) #these inform x and y coordinates

#scootch Bacteria to the left to get more space in the bottom of the web
#original x and y
#coo[2,1]<-(-14)

#also need to move megabenthos, microzooplankton,loligo, smoothdogfish
coo[24,1]<-6
coo[21,1]<-12
coo[19,1]<-(-2.4)
coo[40,1]<-6.5
coo[38,1]<-10

#use ggnetwork to create a network geometry
#storage and flows from original model
n_MAB<-ggnetwork(orig.network_MAB,layout=coo,weights="flow")
#bind with TL info
TL<-as.data.frame(cbind(MAB.rpath$TL,groups_MAB)) %>% rename(vertex.names=groups_MAB,TL=V1)
TL<-TL %>% mutate(TL = as.numeric(TL)) %>% mutate(TL = round(TL,2))
n_MAB<-left_join(n_MAB,TL,by="vertex.names")

#GOM
#pull group list
groups_GOM<-GOM$Group
#Count number of each group type
nliving <- nrow(GOM.params$model[Type <  2, ])
ndead   <- nrow(GOM.params$model[Type == 2, ])

A<-enaStructure(orig.network_GOM)$A
g<-igraph::graph_from_adjacency_matrix(A)

#get x and y coordinates
#derived from the plotfw function (https://rfrelat.github.io/BalticFoodWeb.html)
nylevel<-7 #determines number of levels along y-axis
n <- vcount(g) #number of vertices
tl<-GOM$TL[1:(nliving+ndead)] #pull trophic level calculations from rpath
bks <- c(0.9, seq(1.9, max(tl), length.out = nylevel))
ynod <- cut(tl, breaks = bks, include.lowest = TRUE, 
            labels = 1:(length(bks)-1)) #assign group to a y-level
maxx <- max(table(ynod)) #looks for max # of groups at any y-level
xnod <- rep(0,n)
for (i in 1:nylevel){
  l <- sum(ynod==i)
  
  ltr <- (l/maxx)**(1/2)*maxx
  if (l>1) {
    xnod[ynod==i] <- seq(-ltr,ltr,length.out = l)
  } else {
    xnod[ynod==i] <- 0
  }
}

coo <- cbind(xnod,tl) #these inform x and y coordinates

#move groups manually as needed
coo[2,1]<-(-10)
coo[31,1]<-7
coo[48,1]<-16

#use ggnetwork to create a network geometry
#storage and flows from original model
n_GOM<-ggnetwork(orig.network_GOM,layout=coo,weights="flow")
#bind with TL info
TL<-as.data.frame(cbind(GOM$TL,groups_GOM)) %>% rename(vertex.names=groups_GOM,TL=V1)
TL<-TL %>% mutate(TL = as.numeric(TL)) %>% mutate(TL = round(TL,2))
n_GOM<-left_join(n_GOM,TL,by="vertex.names")

#adjust Detritus storage so it doesn't swamp everything
det_MAB<-max(MAB.rpath$Biomass)
det_GOM<-max(GOM$Biomass)
n_MAB<-n_MAB %>% mutate(storage_adjust = ifelse(storage == det_MAB,100,storage))
n_MAB <- n_MAB %>% mutate(storage_adjust = ifelse(storage < 0.05,0.05,storage_adjust))
n_GOM <- n_GOM %>% mutate(storage_adjust = ifelse(storage < 0.05,0.05,storage))
n_GOM <- n_GOM %>% mutate(storage_adjust = ifelse(storage == det_GOM,100,storage))

GOM_web<-ggplot(n_GOM,aes(x, y, xend = xend, yend = yend)) +
  geom_edges(arrow = arrow(length = unit(7, "pt"), type = "open"),
             curvature = 0.15,position="jitter",
             aes(color=TL,linewidth=flow)) +
  scale_color_gradientn(colors = turbo(6))+
  scale_linewidth(range = c(0.15,9))+
  geom_nodelabel(aes(label=vertex.names,size=((storage_adjust))),show.legend = F) +
  scale_size(range=c(2.5,10))+
  guides(linewidth="none")+
  annotate("text",x=0.025,y=0.975,label="GOM",size=9)+
  theme_blank(legend.position="none")+
  theme_blank(legend.position=c(0.8,0.2))+
  theme(panel.background = element_rect(fill="#EEEEEEFF"),
        plot.background = element_rect(fill="#EEEEEEFF"),
        legend.background=element_rect(fill="#EEEEEEFF"))

GOM_web

MAB_web<-ggplot(n_MAB,aes(x, y, xend = xend, yend = yend)) +
  geom_edges(arrow = arrow(length = unit(7, "pt"), type = "open"),
             curvature = 0.15,position="jitter",
             aes(color=TL,linewidth=flow)) +
  #scale_color_viridis(option = "turbo")+
  scale_color_gradientn(colors = turbo(6))+
  scale_linewidth(range = c(0.15,9))+
  geom_nodelabel(aes(label=vertex.names,size=((storage_adjust))),show.legend = F) +
  scale_size(range=c(2.5,10))+
  guides(linewidth="none")+
  annotate("text",x=0.025,y=0.975,label="MAB",size=9)+
  theme_blank(legend.position=c(0.9,0.15))+
  theme(panel.background = element_rect(fill="#EEEEEEFF"),
        plot.background = element_rect(fill="#EEEEEEFF"),
        legend.background=element_rect(fill="#EEEEEEFF"))

MAB_web
```
##4.3 Figure 3: Flow metric comparisons (bounded to unbounded)
```{r}
#define groups of interest
ks_sig<-ks_flow %>% filter(p<0.001)

flow %>% filter(group %in% ks_sig$Group) %>%
  ggplot(aes(x=flow,fill=condition))+
  geom_density(alpha = 0.4)+
  facet_wrap(vars(group),nrow = 3,scales = "free")
```

##4.4 Figure 4: A/C plots
```{r}
#set color palette
my.pal<-brewer.pal(8,"Set2")
ggplot(data=ASC.CAP,aes(x=ASC.CAP,fill=condition))+
  geom_density(alpha=0.4)+
  geom_vline(xintercept=info.orig_GOM$ASC.CAP,color=my.pal[4],linetype="dashed",linewidth=1)+
  geom_vline(xintercept = 0.39,color="navy",linetype="dashed",linewidth=1)+
  labs(x="A/C",y="density")
```



